Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-20 analysis/paper/paper.Rmd
state that molecular focus was dropped
Revert "fixes theme_classic() set 2X, "
This reverts commit 7ec6b00c9b2200cdd4eb42436378843a70ea4150.

@@

load(file = here("inst/extdata/m_e.Rda"))
load(file = here("inst/extdata/m_f.Rda"))
load(file = here("inst/extdata/m_g.Rda"))
load(file = here("inst/extdata/m_h.Rda"))
load(file = here("inst/extdata/m_i.Rda"))
load(file = here("inst/extdata/m_j.Rda"))
load(file = here("inst/extdata/m_k.Rda"))

pp_m_e <- pp_check(m_e)
pp_m_f <- pp_check(m_f)
pp_m_g <- pp_check(m_g)
pp_m_h <- pp_check(m_h)
pp_m_i <- pp_check(m_i)
pp_m_j <- pp_check(m_j)
pp_m_k <- pp_check(m_k)

# put them all together
p <- (pp_m_e | pp_m_f) / (pp_m_g | pp_m_h) / (pp_m_i | pp_m_j) / pp_m_k

>>>>

Due to differences in evaluators' interpretations (Fig ZZZZ) of whether or not an article had a molecular focus or not, this scoring criteria was not used in the overall evaluation.

@@

load(file = here("inst/extdata/m_f.Rda"))
load(file = here("inst/extdata/m_g.Rda"))
load(file = here("inst/extdata/m_h.Rda"))
load(file = here("inst/extdata/m_i.Rda"))
load(file = here("inst/extdata/m_j.Rda"))
load(file = here("inst/extdata/m_k.Rda"))

pp_m_f <- pp_check(m_f)
pp_m_g <- pp_check(m_g)
pp_m_h <- pp_check(m_h)
pp_m_i <- pp_check(m_i)
pp_m_j <- pp_check(m_j)
pp_m_j <- pp_check(m_k)

# put them all together
p <- (pp_m_f | pp_m_g) / (pp_m_h | pp_m_i) / (pp_m_j | pp_m_k)
